AdaptiveConformal: An `R` Package for Adaptive Conformal Inference

### 2023-11-30 paper.qmd
Updated references

```{r case_study, cache = TRUE}
raw_data <- read_csv("https://raw.githubusercontent.com/FluSightNetwork/cdc-flusight-ensemble/master/scores/point_ests.csv", show_col_types = FALSE)

>>>>

```{r case_study, cache = TRUE}
url <- "https://raw.githubusercontent.com/FluSightNetwork/cdc-flusight-ensemble/master/scores/point_ests.csv"
raw_data <- read_csv(url, show_col_types = FALSE)
